SylvanSeeds, a seed germination database for temperate deciduous forests

### 2020-11-12 README.Rmd
revised folder structure 🍂

![SylvanSeeds](data/2017070313 Blue Ridge Parkway small.jpg)

@@

* `data` Original raw files including the primary result of the search in the Web of Science, and search notes.
* `doc` Files to create the [manuscript](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/manuscript.md) using `Rmarkdown`.
* `results` Output of the `R` scripts, including the clean database and files needed to create the manuscript.
* `src` Scripts in `R` language used to clean the raw data, perform the analyses of the manuscript, and build the `SylvanSeeds` app.

>>>>

![SylvanSeeds](2017070313 Blue Ridge Parkway small.jpg)

@@

* `data` Primary data files including the SylvanSeeds database in csv format and Boolean search string used in the Web of Science.
* `doc` Files to create the [manuscript](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/manuscript.md) using `Rmarkdown`.
* `results` Output of the `R` scripts, including files needed to create the manuscript and run the app.
* `src` Scripts in `R` language used to clean data, perform analyses, and build the `SylvanSeeds` app data.

### 2020-11-12 doc/manuscript.Rmd
revised folder structure 🍂

The database is provided as a *csv* file, comma separated [(**Appendix S5**)](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/TBMF_Database.csv). The first row of the file contains the header data, with the following variables: *Taxon* (the original species names, as used in the references), *TPLName* (*The Plant List* species names), *Family* (the botanical family of the species), *Reference* (bibliographic source of the record), *Year* (year the seed lot was collected), *Country* (country where the seed lot was collected), *Population* (geographical information of the seed lot), *Latitude* (approximated latitude where the seed lot was collected, in decimal degrees), *Longitude* (approximated longitude where the seed lot was collected, in decimal degrees), *Dry_storage* (binary variable indicating whether the seed lot was kept at dry storage for more than a month between seed collection and start of the experiments), *Setting* (environs used to control germination temperature: either a greenhouse, a climatically-controlled incubator, or room temperature), *Sterilization* (note on surface sterilization treatments applied to the seed lot before the experiments), *Nutrients* (note on nutrient application to the germination substrate), *Substrate* (substrate used to hold the seeds during the germination incubation), *Container_type* (type of container used to hold the substrate and the seeds during the experiments), *Container_size* (dimensions of the germination containers), *Container_number* (number of germination containers used for the treatment), *Number_per_container* (number of seeds sown in each container), *Incubation_days* (number of days between the start of the experiment, not including stratification, and the last day when germinated seeds were counted), *Scarification* (binary variable indicating whether the seed lot was scarified before the test), *Stratification_days* (number of days the seed lot was exposed to any type of stratification, before the test), *Stratification_temperature* (temperature or temperatures used during the stratification treatment, in degrees Celsius), *Stratification_type* (type of stratification, which can be none, cold, warm or combinations of cold and warm), *Stratification* (binary variable indicating whether the seed lot was stratified or not before the test), *Light* (binary variable indicating whether the seed lot was germinated in light or in darkness), *Photoperiod* (number of hours of exposure to light in the daily photoperiod), *Alternating* (binary variable indicating whether the germination test was conducted under constant or alternating temperatures), *Tdif* (difference in degrees between the hottest and the coldest temperatures of the daily thermoperiod), *Tmax* (hottest temperature in the daily thermoperiod), *Tmin* (coldest temperature in the daily thermoperiod), *Tmean* (mean germination temperature, weighted by the length of each phase of the daily thermoperiod), *Temperature* (aggregation of the mean germination temperature in 5 ºC intervals), *Germinated* (count of seeds that germinated during the experiment), *Number_seeds* (count of seeds used in the experiment). Each row below the header represents a record for a seed lot germinated in a given set of experimental conditions. Presenting the response variable as a proportion (i.e. number of successes *Germinated*, number of trials *Number_seeds*) has important benefits for meta-analysis of the database, as proportions can be analysed directly using a GLM, and a variance term does not need to be specified since it is incorporated as part of the analysis [@RN4751].

@@

[**Appendices S1-S4**](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/Appendices%20S1-S4.pdf) PRISMA 2009 flow chart describing the process of reference screening and inclusion; bibliography in BibTeX format listing the not-found full texts, the non-relevant references and the relevant references included in the *SylvanSeeds* database.  [**Appendix S5**](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/TBMF_Database.csv) *SylvanSeeds* database in a single *.csv* file.

@@

All persons can use the database providing they cite this paper properly in any publications or in the metadata of any derived products that are produced using the database. The database is provided as [**Appendix S5**](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/TBMF_Database.csv) of this manuscript, but please do visit https://efernandezpascual.github.io/home/sylvanseeds.html to check for updates. It can be visualized with the *SylvanSeeds* app at  https://efernandezpascual.shinyapps.io/sylvanseeds/. The code to create this manuscript and the app is stored at https://github.com/efernandezpascual/sylvanseeds. A version of record of the repository can be found at https://doi.org/10.5281/zenodo.4081377.

>>>>

The database is provided as a *csv* file, comma separated [(**Appendix S5**)](https://github.com/efernandezpascual/sylvanseeds/blob/master/data/TBMF_Database.csv). The first row of the file contains the header data, with the following variables: *Taxon* (the original species names, as used in the references), *TPLName* (*The Plant List* species names), *Family* (the botanical family of the species), *Reference* (bibliographic source of the record), *Year* (year the seed lot was collected), *Country* (country where the seed lot was collected), *Population* (geographical information of the seed lot), *Latitude* (approximated latitude where the seed lot was collected, in decimal degrees), *Longitude* (approximated longitude where the seed lot was collected, in decimal degrees), *Dry_storage* (binary variable indicating whether the seed lot was kept at dry storage for more than a month between seed collection and start of the experiments), *Setting* (environs used to control germination temperature: either a greenhouse, a climatically-controlled incubator, or room temperature), *Sterilization* (note on surface sterilization treatments applied to the seed lot before the experiments), *Nutrients* (note on nutrient application to the germination substrate), *Substrate* (substrate used to hold the seeds during the germination incubation), *Container_type* (type of container used to hold the substrate and the seeds during the experiments), *Container_size* (dimensions of the germination containers), *Container_number* (number of germination containers used for the treatment), *Number_per_container* (number of seeds sown in each container), *Incubation_days* (number of days between the start of the experiment, not including stratification, and the last day when germinated seeds were counted), *Scarification* (binary variable indicating whether the seed lot was scarified before the test), *Stratification_days* (number of days the seed lot was exposed to any type of stratification, before the test), *Stratification_temperature* (temperature or temperatures used during the stratification treatment, in degrees Celsius), *Stratification_type* (type of stratification, which can be none, cold, warm or combinations of cold and warm), *Stratification* (binary variable indicating whether the seed lot was stratified or not before the test), *Light* (binary variable indicating whether the seed lot was germinated in light or in darkness), *Photoperiod* (number of hours of exposure to light in the daily photoperiod), *Alternating* (binary variable indicating whether the germination test was conducted under constant or alternating temperatures), *Tdif* (difference in degrees between the hottest and the coldest temperatures of the daily thermoperiod), *Tmax* (hottest temperature in the daily thermoperiod), *Tmin* (coldest temperature in the daily thermoperiod), *Tmean* (mean germination temperature, weighted by the length of each phase of the daily thermoperiod), *Temperature* (aggregation of the mean germination temperature in 5 ºC intervals), *Germinated* (count of seeds that germinated during the experiment), *Number_seeds* (count of seeds used in the experiment). Each row below the header represents a record for a seed lot germinated in a given set of experimental conditions. Presenting the response variable as a proportion (i.e. number of successes *Germinated*, number of trials *Number_seeds*) has important benefits for meta-analysis of the database, as proportions can be analysed directly using a GLM, and a variance term does not need to be specified since it is incorporated as part of the analysis [@RN4751].

@@

[**Appendices S1-S4**](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/Appendices%20S1-S4.pdf) PRISMA 2009 flow chart describing the process of reference screening and inclusion; bibliography in BibTeX format listing the not-found full texts, the non-relevant references and the relevant references included in the *SylvanSeeds* database.  [**Appendix S5**](https://github.com/efernandezpascual/sylvanseeds/blob/master/data/TBMF_Database.csv) *SylvanSeeds* database in a single *.csv* file.

@@

All persons can use the database providing they cite this paper properly in any publications or in the metadata of any derived products that are produced using the database. The database is provided as [**Appendix S5**](https://github.com/efernandezpascual/sylvanseeds/blob/master/data/TBMF_Database.csv) of this manuscript, but please do visit https://efernandezpascual.github.io/home/sylvanseeds.html to check for updates. It can be visualized with the *SylvanSeeds* app at  https://efernandezpascual.shinyapps.io/sylvanseeds/. The code to create this manuscript and the app is stored at https://github.com/efernandezpascual/sylvanseeds. A version of record of the repository can be found at https://doi.org/10.5281/zenodo.4081377.
